Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-08-29 manuscript/main.tex
update table 2
update table 3
add future prediction as table 4

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|r|r|}
      \hline\hline
      \textbf{Age group} & \multicolumn{2}{c}{\textbf{0 to 120 months}} & \multicolumn{2}{c}{\textbf{0 to 6 months}} & \multicolumn{2}{c}{\textbf{18 to 120 months}} \\ \hline
      geneset & E.S. & q value & E.S. & q value & E.S. & q value \\\hline
      Acetate syn. I & -0.122 & 0.555 & -0.194 & \color{blue}{\textbf{0.153}} & 0.127 & 0.602 \\
      Acetate syn. II & -0.22 & \color{blue}{\textbf{0.066}} & -0.342 & \color{blue}{\textbf{0.02}} & -0.095 & 0.92 \\
      Acetate syn. III & -0.21 & \color{blue}{\textbf{0.086}} & -0.31 & \color{blue}{\textbf{0.052}} & -0.086 & 0.92 \\
      Glutamate deg. I & -0.404 & \color{blue}{\textbf{0.18}} & -0.284 & 0.816 & -0.249 & 0.602 \\
      Glutamate syn. II & 0.095 & 0.602 & -0.134 & 0.98 & 0.242 & \color{red}{\textbf{0.047}} \\
      Menaquinone syn. I & -0.085 & 0.563 & -0.083 & 0.816 & -0.17 & \color{blue}{\textbf{0.182}} \\
      Propionate deg. I & -0.461 & \color{blue}{\textbf{0.13}} & -0.542 & \color{blue}{\textbf{0.02}} & -0.674 & \color{blue}{\textbf{0.041}} \\
      Propionate syn. I & -0.334 & 0.555 & -0.32 & 0.571 & -0.676 & \color{blue}{\textbf{0.023}} \\
      Tryptophan syn. & 0.057 & 0.974 & -0.072 & 0.816 & 0.119 & \color{red}{\textbf{0.041}} \\\hline\hline
    \end{tabular}
    \caption{\label{tab:fsea}Feature set enrichment analysis on neuroactive microbial gene sets.
    Red and blue text indicates significant (q value \textless 0.2) genesets with a positive or negative
    pseudomedian, respectively.}
    \end{center}
\end{table}

@@

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set RMSE (± C.I.)} & \textbf{Test set correlation (± C.I.)} \\\hline
      \multirow{5}{*}{0 to 6} & - & + & 13.01 ± 0.05 & -0.14 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{taxa} & - & 12.66 ± 0.05 & -0.1 ± 0.01 \\ \cline{3-5}
            &       & + & 12.7 ± 0.05 & -0.12 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 12.56 ± 0.05 & -0.01 ± 0.01 \\ \cline{3-5}
            &       & + & 12.56 ± 0.05 & -0.02 ± 0.01 \\ \cline{1-5}
      \multirow{5}{*}{18 to 120} & - & + & 16.27 ± 0.04 & 0.506 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{taxa} & - & 17.66 ± 0.04 & 0.363 ± 0.003 \\ \cline{3-5}
            &       & + & 17.29 ± 0.04 & 0.429 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 18.01 ± 0.04 & 0.303 ± 0.003 \\ \cline{3-5}
            &       & + & 17.86 ± 0.04 & 0.333 ± 0.004 \\\hline\hline
    \end{tabular}
    \caption{\label{tab:rfbench}Benchmark metrics for the cognitive assessment score
    prediction models. Confidence intervals (C.I.) are calculated from the
    distribution of metrics from repeated CV at a confidence level of 95.
    Root mean square error (RMSE) was used to estimate how well the random forest model was able to predict the outcome.
    Demo. column indicates whether demographic factors such as maternal education, sex and age were included as predictors.}
    \end{center}
\end{table}

>>>>

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|r|r|}
      \hline\hline
      \textbf{Age group} & \textbf{under 6m} & \textbf{under 6m} & \textbf{over 18m} & \textbf{over 18m} \\
      \texttt{geneset} & \texttt{E.S.} & \texttt{q value} & \texttt{E.S.} & \texttt{q value} \\\hline
      Acetate syn. I & -0.21 & \color{red}{\textbf{0.068}} & 0.123 & 0.403 \\
      Acetate syn. II & -0.322 & \color{red}{\textbf{0.046}} & 0.113 & 0.866 \\
      Acetate syn. III & -0.291 & \color{red}{\textbf{0.089}} & 0.109 & 0.866 \\
      Glutamate syn. II & -0.152 & 0.882 & 0.293 & \color{blue}{\textbf{0.001}} \\
      Propionate deg. I & -0.639 & \color{red}{\textbf{0.006}} & -0.495 & 0.446 \\\hline\hline
    \end{tabular}
    \caption{\label{tab:fsea}Feature set enrichment analysis on neuroactive microbial gene sets.
    Red and blue text indicates significant (q value \textless 0.2) genesets with a positive or negative
    pseudomedian, respectively.}
    \end{center}
\end{table}

@@

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set RMSE (± C.I.)} & \textbf{Test set correlation (± C.I.)} \\\hline
      \multirow{5}{*}{0 to 6} & -    & + & 13.37 ± 0.05 & -0.16 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 12.99 ± 0.04 & -0.11 ± 0.01 \\ \cline{3-5}
            &                        & + & 13.01 ± 0.04 & -0.13 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{3-5}
            &                        & + & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{1-5}
      \multirow{5}{*}{18 to 120} & - & + & 17.06 ± 0.04 & 0.511 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 18.71 ± 0.04 & 0.347 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.25 ± 0.04 & 0.429 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 18.96 ± 0.04 & 0.299 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.74 ± 0.04 & 0.341 ± 0.003 \\ \hline\hline
    \end{tabular}
    \caption{\label{tab:rfbench}Benchmark metrics for the cognitive assessment score
    prediction models. Confidence intervals (C.I.) are calculated from the
    distribution of metrics from repeated CV at a confidence level of 95.
    Root mean square error (RMSE) was used to estimate how well the random forest model was able to predict the outcome.
    Demo. column indicates whether demographic factors such as maternal education, sex and age were included as predictors.}
    \end{center}
\end{table}

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r}
        \hline
        \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set correlation (± C.I.)} & \textbf{Test set Root-mean-square error (± C.I.)} \\\hline
        - & + & 20.25 ± 0.07 & 0.43 ± 0.0 \\ \cline{1-4}
        \multirow{2}{*}{taxa} & - & 22.32 ± 0.08 & 0.07 ± 0.0 \\ \cline{2-4}
            & + & 21.53 ± 0.08 & 0.27 ± 0.0 \\ \cline{1-4}
        \multirow{2}{*}{genes} & - & 22.21 ± 0.08 & 0.12 ± 0.0 \\ \cline{2-4}
            & + & 22.08 ± 0.08 & 0.15 ± 0.0 \\\hline\hline
    \end{tabular}
    \caption{\label{tab:rfbench}Benchmark metrics for the cognitive assessment score
    future prediction models. Confidence intervals (C.I.) are calculated from the
    distribution of metrics from repeated CV at a confidence level of 95.
    Root mean square error (RMSE) was used to estimate how well the random forest model was able to predict the outcome.
    Demo. column indicates whether demographic factors such as maternal education, sex and age were included as predictors.}
    \end{center}
\end{table}
